---
title       : My Lectures
author      : Ramnath Vaidyanathan
framework   : minimal
hitheme     : solarized_light
mode        : selfcontained
github      : {user: slidify, repo: lectureSite, branch: gh-pages}
---

# Course Title 

<a href="http://prose.io/#{{site.github.user}}/{{site.github.repo}}/edit/gh-pages/index.Rmd" class="button icon edit">Edit Page</a>

```{r setup, cache = F, echo = F}
knitr::knit_hooks$set(document = function(doc){
  gsub('`` ', '```', doc)
})
```


This is a template for creating a quick website for a course using Slidify. Once you have configured `site.yml`, edited your `Rmd` source files, all you need to do is to run `blogify(".")` from the root. Slidify will automatically detect all the `Rmd` files, slidify them, and create all lecture slides along with the index page. 

This sample course website, was actually generated the exact same way!

## Structure

The first thing to understand is the folder structure. The `lectures` folder holds your lecture slides, one subfolder per lecture. 

```
assets      -> put custom img/js/css/layout assets
lectures    -> folder containing lectures
  01
  02
  03
libraries   -> frameworks, highlighters and widgets
index.Rmd   -> Rmd source for home page
site.yml    -> Site related configuration
```

## Configuration

The file `site.yml` contains properties that need to be customized. A property named `foo` in `site.yml` can be accessed in any of the layout files as `site.foo`.

## Navigation

It is easy to automatically add a list of lectures by adding the following code chunk to your `index.Rmd`. It assumes that you are using the same folder structure and naming scheme. If you use a different scheme, make sure that you tweak the code in this code chunk.

    `` {r echo = F, results = 'asis'}
    lectures = dir('lectures', full = TRUE)
    links = paste0(seq_along(lectures), ". ", 
      "[Lecture ", basename(lectures), "]", "(", lectures, "/index.html)"
    )
    writeLines(links)
    ```

This is the output from running the above code chunk.

```{r echo = F, results = 'asis'}
lectures = dir('lectures', full = TRUE)
links = paste0(seq_along(lectures), ". ", 
  "[Lecture ", basename(lectures), "]", "(", lectures, "/index.html)"
)
writeLines(links)
```

## Features

One nice feature you will notice is that all lecture slides automatically get an `edit` button, that when clicked opens up the `Rmd` source in `prose.io`. This makes it easy for people to correct typos, and contribute to your lecture slides.

<a href='lectures/01/#3'>
   <img style='border: 1px solid;' width=100% src=http://www.clipular.com/c?14735047=rpmipgzz3PAoKUVW7jQ4hE30iKk&f=.png></img>
</a>







